---
title: "Anomaly Detection"
author: "Roselynn"
date: "1/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Importing the Dataset and loaded the appropriate packages

I loaded the anomalize() package which is used in anomaly detection and the tidyverse package.

```{r}

library(anomalize)
library(tidyverse)
library(tibbletime)

```

I imported the dataset then previewed it 

```{r}


dataset <- read.csv("http://bit.ly/CarreFourSalesDataset")
head(dataset)
tail(dataset)
View(dataset)
```

The dataset had two columns , the Date column was of type character so I converted it to date format using the as.Date function.


```{r}

dataset$Date <- as.Date(dataset$Date , format = "%m/%d/%Y")
head(dataset)
unique(dataset$Date)

dataset <- as_tbl_time(dataset , index= Date)
```

I plotted all the Sales made in my dataset.

```{r}

viz <- dataset %>%  
  ggplot(aes(x = Date, y = Sales)) +
  geom_line(col = "blue") +
  ggtitle("Sales from Jan - April") +
  labs(x = "Date", y = "Sales")

viz


```


I then used the anomalize() function to detect anomalies in my dataset.

```{r}

 dataset %>%
  group_by(Date) %>%
  summarise(Orders = sum(Sales)) %>%
  time_decompose(Orders, method = "twitter", frequency = "auto", trend = "auto") %>%
  anomalize(remainder, method = "gesd",alpha = 0.05, max_anoms = 0.2) %>%
  time_recompose() %>%
  # Anomaly Visualization
  plot_anomalies(
  time_recomposed =T,
  ncol = 3,
  color_no = "#2c3e50",
  color_yes = "#e31a1c",
  fill_ribbon = "grey70",
  size_dots = 2,
  size_circles = 4)

```



I visualized the decomposition using plot_anomaly_decomposition().


```{r , fig.width=7,fig.height=7}

 dataset %>%
  group_by(Date) %>%
  summarise(Orders = sum(Sales)) %>%
  time_decompose(Orders, method = "twitter", frequency = "auto", trend = "auto") %>%
  anomalize(remainder,method = "gesd", alpha = 0.05, max_anoms = 0.2) %>%
  time_recompose() %>%
  # Anomaly Visualization
  plot_anomaly_decomposition()

```

# Summary

My model detected anomalies within the dataset.

