---
title: "Association Rules - Week 14"
author: "Roselynn"
date: "1/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.Loading the Packages and Importing the Dataset

I loaded the tidyverse package and the arules package

```{r}

library(arules)
library(tidyverse)

```

I imported the dataset using the read.transactions() function

```{r}

# Importing the Dataset

dataset <- read.transactions("http://bit.ly/SupermarketDatasetII" ,  
                                   sep =",")
#View(dataset)
```

I used the summary function to obtain the summary statisics of the dataset.

```{r}

summary(dataset)

```
The dataset had 119 items with 7501 itemsets with the most frequently purchased item being mineral water.


I then previewed the first ten itemsets using the inspect function

```{r}
inspect(dataset[1:10])

```


I also previewed the items in my dataset.

```{r}

items <- as.data.frame(itemLabels(dataset))
colnames(items) <- "Item"
head(items, 10)    
tail(items,10)
```


I then inspected the frequency of the first 15 items in my dataset.

```{r}

itemFrequency(dataset[, 1:15],type = "absolute")

``` 

I plotted the top 20 most frequent items in the dataset using the ItemFrequency and topN.

```{r}

itemFrequencyGGPlot <- function(x, topN) {
  library(tidyverse)
  x %>%
    itemFrequency %>%
    sort %>%
    tail(topN) %>%
    as.data.frame %>%
    tibble::rownames_to_column() %>%
    ggplot(aes(reorder(rowname, `.`),`.`)) + 
    geom_col(fill='cyan4') + labs(title='20 most frequently bought Items in the Dataset' , y  = "Frequency" , x = 'Items')+
    coord_flip()
}  
itemFrequencyGGPlot(dataset, 20)

```

The most frequent label within the whole dataset was the Mineral water , followed by eggs.


# Association Rules

I then obtained the rules of the dataset using the apriori()  function.

```{r}

rules <- apriori (dataset, parameter = list(supp = 0.001, conf = 0.6))
rules

```

I set my support as 0.001 and my confidence as 0.7 , I got 200 rules from the dataset 

I then used the inspect function to see the first 10 rules of my dataset

```{r}
inspect(rules[1:10])

```


Similarly I did the same for the last ten rules 

```{r}
inspect(rules[535:545])

```

I used the quality() function to check the quality of the rules of my model.

```{r}

head(quality(rules))

```

```{r}

tail(quality(rules))

```

# Visualizing association rules using the arulesviz package

In order to gain more insights from my model , I used the arulesviz package to visualize the first fifteen rules created from the parameters of my model.

```{r}
#install.packages("arulesViz")
library(arulesViz)

```




```{r}

## Scatterplot with custom colors
library(colorspace) 
# for sequential_hcl
plot(rules)

```


I noted that there was one rule with high lift , it also had low confidence and low support


I created a subrules variable that had the first thirty rules of the model.
I used the htmlwidget to create an interactive plot of the subrules.

```{r , fig.width=10,fig.height=10}

subrules <- head(rules, n = 30, by = "confidence")

plot(subrules, method = "graph" ,   engine = "htmlwidget")


```
For instance from rule 15 , people buying cake , meatballs and milk were also likely to buy mineral water.

I also plotted the graph , with the default engine.
Many arrows tend to point towards the Mineral water , meaning many of the purchases were associated with the purchase of mineral water.

```{r , fig.width=15,fig.height=15}

plot(subrules, method = "graph" ,   engine = "default")


```

I also used the paracoord method to plot out my subrules

```{r , fig.width=10,fig.height=10}

plot(subrules, method = "paracoord")

```
Finally I plotted my subrules with the grouped method

```{r , fig.width=10,fig.height=10}



## 2D matrix with shading
plot(subrules,method="grouped", measure="confidence", engine ="default" )


```

# Summary 

From my grouped plot I noted that Mineral water had an association with many of the items , for instance from this plot above it had :
 + 1 rule with whole wheat , pasta and turkey with low lift and low confidence.
  + 2 rules with nonfat milk , chocolate and four other items with low lift and low confidence.
  + 6 rules with brownies , chicken and 14 other items , with low lift and low confidence.
  
  
The rules with the highest confidence were :

+ Olive oil , light cream with three other items and mineral water.
+ Meatball , cake and one other item with milk
+ Mushroom Cream Sauce and Pasta with escalope
+ Mushroom Cream Sauce , French fries and one other item with escalope

The rules with high lift were :

+ Eggs , Pasta and one other item with shrimp
+ Mushroom Cream Sauce , French fries and one other item with escalope
+ Pasta , milk with shrimp 
+ Mushroom Cream Sauce and Pasta with escalope

```{r , fig.width=10,fig.height=10}



## 2D matrix with shading
plot(subrules,method="grouped", measure="support", engine ="default" )


```
I plotted the same graph , using the support in place of the confidence and similar results can be echoed here.