---
title: "Feature_Selection"
author: "Roselynn"
date: "1/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Importing the Dataset and Loading the Appropriate Packages.

I first loaded the tidyverse package and then imported my dataset 

```{r}

library(tidyverse)
library(caret)

```



```{r}

dataset <- read.csv("http://bit.ly/CarreFourDataset")

```

I then used the glimpse() function to preview my dataset

```{r}

glimpse(dataset)

```

The dataset had 16 columns , 8 of type character and 8 numeric columns.





# 2.Data Cleaning

I then used the summary() function to get the summary statistics of the columns in my dataset.

```{r}

summary(dataset)

```

### 2.1.Checking for Null Values 

I checked for any null entries , the dataset had none

```{r}

sum(is.na(dataset))

```


```{r}

sum(duplicated(dataset))

```



# 3.Feature Selection

## 3.1.Filter Method

The used the correlation coefficient to filter out the highly correlated freatures from the dataset.

```{r}

dataset <- select(dataset , -1,-2,-3,-4,-5,-9,-10,-11,-13)
head(dataset)

```


I used the Pearson's Correlation Coefficient and set a cutoff of 0.75 , features with a correlation coefficient greater that 0.75 were then excluded from the model.

```{r}
# Calculating the correlation matrix

correlationMatrix <- cor(dataset)


library(ggcorrplot)
library(corrplot)

ggcorrplot(correlationMatrix ,hc.order=F,lab=T, type = 'upper' , tl.srt=90 , ggtheme = ggplot2::theme_gray, )

```



```{r}
# Find attributes that are highly correlated

highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.75)

# Highly correlated attributes

highlyCorrelated

names(dataset[,highlyCorrelated])

```

The highly correlated features in this dataset were the Cogs , Total and Tax features with a correlation coefficient of 1.




```{r , fig.width=10,fig.length=10}

# We can remove the variables with a higher correlation 
# and comparing the results graphically as shown below
# ---
# 
# Removing Redundant Features 
# ---
# 
Dataset2<-dataset[-highlyCorrelated]

# Performing our graphical comparison
# ---
# 
par(mfrow = c(1, 2))
corrplot(correlationMatrix, order = "hclust")
corrplot(cor(Dataset2), order = "hclust")

```

## 3.2.Wrapper Method


```{r}

Dataset <- read.csv("http://bit.ly/CarreFourDataset")
Dataset <- select(Dataset , -1,-2,-3,-4,-5,-9,-10,-11,-13)
head(Dataset)

```


```{r}
# Sequential forward greedy search (default)
# ---
#
library(clustvarsel)
library(mclust)
out = clustvarsel(Dataset)
out

```


```{r}
# The selection algorithm would indicate that the subset 
# we use for the clustering model is composed of variables X1 and X2 
# and that other variables should be rejected. 
# Having identified the variables that we use, we proceed to build the clustering model:
# ---
#

Subset1 = Dataset[,out$subset]
mod = Mclust(Subset1)
summary(mod)

```


```{r}
plot(mod,c("classification"))

```
