---
title: "Feature_Selection"
author: "Roselynn"
date: "1/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Importing the Dataset and Loading the Appropriate Packages.

I first loaded the tidyverse package and then imported my dataset 

```{r}

library(tidyverse)
library(caret)

```



```{r}

dataset <- read.csv("http://bit.ly/CarreFourDataset")

```

I then used the glimpse() function to preview my dataset

```{r}

glimpse(dataset)

```

The dataset had 16 columns , 8 of type character and 8 numeric columns.





# 2.Data Cleaning

I then used the summary() function to get the summary statistics of the columns in my dataset.

```{r}

summary(dataset)

```

### 2.1.Checking for Null Values 

I checked for any null entries , the dataset had none

```{r}

sum(is.na(dataset))

```


```{r}

sum(duplicated(dataset))

```



# 3.Feature Selection

## 3.1.Filter Method

The used the correlation coefficient to filter out the highly correlated features from the dataset.

```{r}

dataset <- select(dataset , -1,-2,-3,-4,-5,-9,-10,-11,-16,-13)
head(dataset)

```
I selected the continuous variables within my dataset , however I did not select the Total , as this was the target variable in the dataset.
I also dropped the Gross.margin.percentage as the columnn had a constant value and was therefore redundant.

I used the Pearson's Correlation Coefficient and set a cutoff of 0.75 , features with a correlation coefficient greater that 0.75 were then excluded from the model.

```{r}
# Calculating the correlation matrix

correlationMatrix <- cor(dataset)


library(ggcorrplot)
library(corrplot)

ggcorrplot(correlationMatrix ,hc.order=F,lab=T, type = 'upper' , tl.srt=90 , ggtheme = ggplot2::theme_gray, )

```



```{r}
# Find attributes that are highly correlated

highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.75)

# Highly correlated attributes

highlyCorrelated

names(dataset[,highlyCorrelated])

```

The highly correlated features in this dataset were the Cogs and Tax features with a correlation coefficient of 1.


I then dropped these from the dataset.

```{r , fig.width=10,fig.length=10}

# We can remove the variables with a higher correlation 
# and comparing the results graphically as shown below
# ---
# 
# Removing Redundant Features 
# ---
# 
Dataset2<-dataset[-highlyCorrelated]

# Performing our graphical comparison
# ---
# 
par(mfrow = c(1, 2))
corrplot(correlationMatrix, order = "hclust")
corrplot(cor(Dataset2), order = "hclust")

```
After removing the highly correlated features from my dataset I was left with :

 + Rating
 + Unit Price
 + Quantity
 + Gross Income 
As my features.



## 3.2.Wrapper Method

I also attempted to use the Wrapper method to carry out feature selection.

```{r}

Dataset <- read.csv("http://bit.ly/CarreFourDataset")
Dataset <- select(Dataset , -1,-2,-3,-4,-5,-9,-10,-11,-13,-16)
head(Dataset)

```
I wanted to select the best features to use in building my model from the features listed above.

I used the clustvarsel package to carry out the feature selection.

```{r}
# Sequential forward greedy search (default)
# ---
#
library(clustvarsel)
library(mclust)
out = clustvarsel(Dataset)
out

```



I then used the selected subset from the features above.

The Selected subset: Quantity, cogs, Unit.price

```{r}


Subset1 = Dataset[,out$subset]
mod = Mclust(Subset1 , G = 1:3)
summary(mod)

```


```{r}
plot(mod,c("uncertainty"))

```
# Summary

After carrying out both methods , the filter method selected four features , the ones that were not highly correlated while the wrapper method selected a subset of three features from the dataset.