---
title: "PCA"
author: "Roselynn"
date: "1/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Importing the Dataset and Loading the Appropriate Packages.

I first loaded the tidyverse package and then imported my dataset 

```{r}

library(tidyverse)

```



```{r}

dataset <- read.csv("http://bit.ly/CarreFourDataset")

```

I then used the glimpse() function to preview my dataset

```{r}

glimpse(dataset)

```

The dataset had 16 columns , 8 of type character and 8 numeric columns.

# 2.Data Cleaning

I then used the summary() function to get the summary statistics of the columns in my dataset.

```{r}

summary(dataset)

```

### 2.1.Checking for Null Values 

I checked for any null entries , the dataset had none

```{r}

sum(is.na(dataset))

```


```{r}

sum(duplicated(dataset))

```



# Principal Component Analysis

```{r}
rownames(dataset)   <- dataset[,1]

```

Finally I selected the numeric columns in my dataset and carried out PCA using the prcomp() function.

```{r}

dataset <- select(dataset , -1,-2,-5,-13,-9,-10,-11)
head(dataset)

```

I selected all the continuous features in my dataset and carried PCA with the prcomp() funtion.

```{r}
pca <- prcomp(dataset[,c(3,5:9)], center = TRUE, scale = TRUE)
summary(pca)

```

After carrying out PCA I noted that the first principal component explained 74.43% of the total variance while the last three components explained 0% of the variance.


Using the str() function , I noted that
```{r}

str(pca)

```

# Plotting the Principal Components

```{r}

library(ggbiplot)
ggbiplot(pca, obs.scale = 0.2, var.scale = 0.5)

```


```{r}

library(ggbiplot)
ggbiplot(pca, obs.scale = 0.5, var.scale = 0.5, groups = dataset$Customer.type,ellipse = TRUE, circle = TRUE)

```
```{r}

library(ggbiplot)
ggbiplot(pca, obs.scale = .05, var.scale = 1, groups = as.factor(dataset$Quantity), ellipse = TRUE, circle = TRUE)

```

